Fuels, fire weather, and Rx fire behavior in North Dakota

### 2021-02-18 writeups/FuelsWeatherFirebehavior.Rmd
robust imputation update

@@

```{r dist_gg, fig.width = 8, fig.height =8, fig.cap = "Gamma distributions are fit to all response variables. Two outliers above 600 deg C were removed from analysis on soil maximum temperature."}
# Distributions of response variables
  ros_dist <-
  AnalysisData %>% 
    ggplot(aes(x=ros)) + theme_bw(14) + 
    geom_histogram(aes(y=..density..),      
                   binwidth=0.5,
                   colour="black", 
                   fill="lightgreen") +
    geom_density(alpha=0.2, 
                 fill="#FF6666") 
  tempC_dist <- 
  AnalysisData %>% 
    ggplot(aes(x=MaxC)) + theme_bw(14) + 
    geom_histogram(aes(y=..density..),      
                   binwidth=10,
                   colour="black", 
                   fill="lightgreen") +
    geom_density(alpha=0.2, 
                 fill="#FF6666") 
  soilC_dist <- 
  AnalysisData %>% 
  ggplot(aes(x=SoilMaxC)) + theme_bw(14) + 
  geom_histogram(aes(y=..density..),      
                 binwidth=10,
                 colour="black", 
                 fill="lightgreen") +
  geom_density(alpha=0.2, 
               fill="#FF6666") 
  gridExtra::grid.arrange(tempC_dist, soilC_dist, 
                          ros_dist, ncol=2)
```

@@

```{r missing_table}
# MICE operations 
#
# Pattern of missing data
AnalysisData %>%
  select(-FireCode, -location, -block, -pasture,-patch,
         -year, -plot, -array) %>%
    mice::md.pattern(plot = F) %>%
  pander::pander(caption="Table of missing values by variable.") 
```

>>>>

Figures generated by the script below and included in this document are [available on GitHub](https://github.com/devanmcg/SpatialFireBehavior/tree/main/writeups/figures), as well.

@@

```{r dist_gg, fig.width = 8, fig.height =8, fig.cap = "Gamma distributions are fit to all response variables. An outlier well above 600 deg C were removed from analysis on soil maximum temperature."}
# Distributions of response variables
  ros_dist <-
  AnalysisData %>% 
    ggplot(aes(x=ros)) + theme_bw(14) + 
    geom_histogram(aes(y=..density..),      
                   binwidth=0.5,
                   colour="black", 
                   fill="lightgreen") +
    geom_density(alpha=0.2, 
                 fill="#FF6666") 
  tempC_dist <- 
  AnalysisData %>% 
    ggplot(aes(x=MaxC)) + theme_bw(14) + 
    geom_histogram(aes(y=..density..),      
                   binwidth=10,
                   colour="black", 
                   fill="lightgreen") +
    geom_density(alpha=0.2, 
                 fill="#FF6666") 
  soilC_dist <- 
  AnalysisData %>% 
  ggplot(aes(x=SoilMaxC)) + theme_bw(14) + 
  geom_histogram(aes(y=..density..),      
                 binwidth=10,
                 colour="black", 
                 fill="lightgreen") +
  geom_density(alpha=0.2, 
               fill="#FF6666") 
  gridExtra::grid.arrange(tempC_dist, soilC_dist, 
                          ros_dist, ncol=2)
```

@@

```{r missing_table}
# MICE operations 
#
# Pattern of missing data
AnalysisData %>%
  select(-FireCode, -location, -block, -pasture,-patch,
         -year, -plot, -array, -LAI) %>%
    mice::md.pattern(plot = F) %>%
  pander::pander(caption="Table of missing values by variable.") 
```
